DRAFT: Week 3: Degree and Centrality

### 2022-04-19 docs/3. SNA - Assignments/DRAFT_Week3-Distill-Blog_Degree-and-Centrality.Rmd
4.12.22

    > 10 most common values are:
    >
    > JUICE : 135 , RUM: 125, SYRUP: 115, LIQUEUR
    > : 84 , BITTERS: 54 ,
    >
    > SODA : 28 , SPICE: 19, GIN: 12, BRANDY: 9,
    > FRUIT: 7

@@

@@

+-----+---+------+---+------+---+
| deg |   | inde |   | o    |   |
| ree |   | gree |   | utde |   |
|     |   |      |   | gree |   |
+=====+===+======+===+======+===+
| M   | 0 | Min. | 0 | Min. | 0 |
| in. |   |      | . |      |   |
|     |   |      | 0 |      |   |
|     |   |      | 0 |      |   |
|     |   |      | 0 |      |   |
+-----+---+------+---+------+---+
| 1st | 0 | 1st  | 0 | 1st  | 0 |
| Qu. |   | Qu.  |   | Qu.  |   |
+-----+---+------+---+------+---+
| Med | 1 | Me   | 1 | Me   | 0 |
| ian |   | dian |   | dian |   |
+-----+---+------+---+------+---+
| M   | 2 | Mean | 2 | Mean | 2 |
| ean | . |      | . |      | . |
|     | 4 |      | 4 |      | 4 |
|     | 5 |      | 4 |      | 4 |
|     |   |      | 9 |      | 9 |
+-----+---+------+---+------+---+
| 3rd | 2 | 3rd  | 2 | 3rd  | 5 |
| Qu. |   | Qu.  |   | Qu.  |   |
+-----+---+------+---+------+---+
| M   | 6 | Max. | 6 | Max. | 1 |
| ax. | 2 |      | 2 |      | 1 |
+-----+---+------+---+------+---+
|     |   |      |   |      |   |
+-----+---+------+---+------+---+

@@

+-----------+-------------+-----------------+
| degree    | indegree    | outdegree       |
+===========+=============+=================+
| Min:      | Min: 0.000  | Min: 0.000      |
| 1.000     |             |                 |
+-----------+-------------+-----------------+
| 1st Qu:   | 1st Qu:     | 1st Qu: 0.000   |
| 1.000     | 0.000       |                 |
+-----------+-------------+-----------------+
| Median:   | Median:     | Median: 0.000   |
| 4.000     | 1.000       |                 |
+-----------+-------------+-----------------+
| Mean:     | Mean: 2.449 | Mean: 2.449     |
| 4.898     |             |                 |
+-----------+-------------+-----------------+
| 3rd Qu:   | 3rd Qu:     | 3rd Qu: 5.000   |
| 6.000     | 2.000       |                 |
+-----------+-------------+-----------------+
| Max:      | Max: 62.000 | Max: 11.000     |
| 62.000    |             |                 |
+-----------+-------------+-----------------+

@@

#### Degree Centrality: Network vs Node

@@

-   Centralization Score Break Down

>>>>

    > 10 most common values are:
    >
    > JUICE : 135 , RUM: 125, SYRUP: 115, LIQUEUR
    >
    > :   84 , BITTERS: 54 ,
    >
    > SODA : 28 , SPICE: 19, GIN: 12, BRANDY: 9,
    > FRUIT: 7

@@

centr_degree(igEL)\$theoretical_max: 74802

@@

| deg ree |         | inde gree |           | o utde gree |           |
|---------|---------|-----------|-----------|-------------|-----------|
| M in.   | 0       | Min.      | 0 . 0 0 0 | Min.        | 0         |
| 1st Qu. | 0       | 1st Qu.   | 0         | 1st Qu.     | 0         |
| Med ian | 1       | Me dian   | 1         | Me dian     | 0         |
| M ean   | 2 . 4 5 | Mean      | 2 . 4 4 9 | Mean        | 2 . 4 4 9 |
| 3rd Qu. | 2       | 3rd Qu.   | 2         | 3rd Qu.     | 5         |
| M ax.   | 6 2     | Max.      | 6 2       | Max.        | 1 1       |
|         |         |           |           |             |           |

@@

| degree        | indegree      | outdegree     |
|---------------|---------------|---------------|
| Min: 1.000    | Min: 0.000    | Min: 0.000    |
| 1st Qu: 1.000 | 1st Qu: 0.000 | 1st Qu: 0.000 |
| Median: 4.000 | Median: 1.000 | Median: 0.000 |
| Mean: 4.898   | Mean: 2.449   | Mean: 2.449   |
| 3rd Qu: 6.000 | 3rd Qu: 2.000 | 3rd Qu: 5.000 |
| Max: 62.000   | Max: 62.000   | Max: 11.000   |

@@

#### Vetwork Degree Centrality: In's & Out's

Centralization Score Break Down

-   Stat: Overall Network Centrality

-   Stats: 10 most Popular In's & Out's

@@

-

### 2022-04-19 docs/3. SNA - Assignments/sna_Week3/DRAFT-week3-Assignment.Rmd
4.12.22

```{r Statmet: Netweork Centrality:  low & high degree nodes}

#sort to find 5 highest and lowest degree nodes in trade100

network::list.edge.attributes(snEL)

snEL_nodeHeadTail <-data.frame(
  name=snEL%v%"vertex.names",
  indegree=sna::degree(snEL, cmode="indegree"),
  outdegree=sna::degree(snEL, cmode="outdegree"))

snEL_nodeHeadTail%>%
  arrange(desc(indegree))%>%
  slice(1:10)

snEL_nodeHeadTail%>%
  arrange(indegree)%>%
  slice(1:10)

snEL_nodeHeadTail%>%
  arrange(desc(outdegree))%>%
  slice(1:10)

snEL_nodeHeadTail%>%
  arrange(outdegree)%>%
  slice(1:10)

view(snEL_nodeHeadTail)

>>>>

```{r Statnet:Centrality: High Degree Nodes}
library(statnet)
library(sna)
#sort to find 5 highest and lowest degree nodes in trade100

snel_HiStatus<-data.frame(
  name=snEL%v%"vertex.names",
  sna::degree(snEL),
  indegree=sna::degree(snEL, cmode="indegree"),
  outdegree=sna::degree(snEL, cmode="outdegree"))

temp_in <- temp%>%
  arrange(desc(indegree))%>%
  slice(1:10)
temp%>%
  arrange(indegree)%>%
  slice(1:10)

temp_out <- temp%>%
  arrange(desc(outdegree))%>%
  slice(1:10)
temp%>%
  arrange(outdegree)%>%
  slice(1:10)

  summary(temp)
  summary(temp_in)
  summary(temp_out)

```{r Statnet: Centrality: Low Degree Nodes}
library(statnet)
library(sna)
#sort to find 5 highest and lowest degree nodes in trade100

temp <-data.frame(
  name=snEL%v%"vertex.names",
  sna::degree(snEL),
  indegree=sna::degree(snEL, cmode="indegree"),
  outdegree=sna::degree(snEL, cmode="outdegree"))

low_in <- temp%>%
  arrange(tail(indegree))%>%
  slice(1:10)
temp%>%
  arrange(indegree)%>%
  slice(1:10)

low_out <- temp%>%
  arrange(tail(outdegree))%>%
  slice(1:10)
temp%>%
  arrange(outdegree)%>%
  slice(1:10)

  summary(temp)
  summary(low_in)
  summary(low_out)
